Tree Graphs Test

### 2021-07-14 tests/testgraphs.Rmd
Trivial change

```{r}
w2 <- tree_diameter1 %>%
  ggplot(aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_y_discrete(limits=c("Tsuga canadensis", "Quercus rubra"))
w2
```

>>>>

```{r}
w2 <- tree_diameter1 %>%
  ggplot(aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_y_discrete(limits=c("Eastern Hemlock"))
w2
```
